---
title: "Day_1_Interactive_Session_2"
author: "Juliet"
date: "8/2/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

### logs and exponents in R

Some examples of using 'log()' function and 'exp()' **function** in R

```{r}
# Examples of Logarithms 
log(4)

#example of exponent
exp(5)

#a test of log()
log(exp(1))
#this returns 1 because the log and e cancel to return just what is in the ()

```

### Creating sequences of values
```{r}
# a sequence from 1-20 in increments of 1

ex_1 <- seq(from =1, to = 20, by = 1)

# Vector from 0 to 40 in increments of 0.2

ex_2 <- seq(from = 0, to = 40, by = 0.2)

# vector from 1-5000 by increments of 10
ex_3 <- seq (from = 1, to = 5000, by = 0.2)
```


### create function for logistic growth

Given the carrying capacity, the initial pop and the growth rate, and a time, use the logistic growth model to estimate the population at that time

```{r}
pop_logistic <- function(capacity, init_pop, rate, time_yr) {
  capacity/(1+((capacity - init_pop)/(init_pop)) * (exp(-rate * time_yr)))
}

pop_logistic(capacity = 2580, init_pop = 230, rate = 0.32, time_yr = 2.4)

```
### try finding the population over a sequence of times

```{r}
time_vec <- seq(from = 3, to = 15, by = 0.5)
#check your vector
#time_vec

```

Now lets estimate the population over that range of times, given capacity = 2580, initial population = 230, rate = 0.32

```{r}
chipmunk_pop <- pop_logistic(capacity = 2580, init_pop = 230, rate = 0.32, time_yr = time_vec)
chipmunk_pop
#the largest value is 2536 so that makes sense with a carrying capacity of 2580
```

### create data frame and plot chipmunk pop over time

```{r}
#ggplot only wants data frames so need to combine time and pop into a data frame
chipmunk_df <- data.frame(time_vec, chipmunk_pop)
#chipmunk_df

```

### create a bare minimum ggplot graph
```{r}
ggplot(data = chipmunk_df, aes(x = time_vec, y = chipmunk_pop)) +
  geom_point() + 
  labs( x = "time (years)",
        y = "Chipmunk pop (individuals)",
        title = "Inyo NF chipmunks",
        subtitle = "yay chipmunks")
```






